\documentclass[12pt, letterpaper, oneside]{book}
\usepackage{cleveref}

\crefformat{chapter}{\S#2#1#3}
\crefformat{section}{\S#2#1#3} % see manual of cleveref, section 8.2.1
\crefformat{subsection}{\S#2#1#3}
\crefformat{subsubsection}{\S#2#1#3}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead[R,L]{}
\fancyhead[C]{\leftmark}

\makeatletter
\@addtoreset{chapter}{part}
\makeatother

\title{Bylaws and Regulations \\ of \\ the WPI ACM Chapter}
\author{WPI Association for Computing Machinery}
\date{\today}

\begin{document}
\maketitle

\tableofcontents
\newpage

\renewcommand{\chaptername}{Article}

\chapter{Name and Purpose}
\begin{enumerate}
    \item This organization shall be known as the Worcester Polytechnic
        Institute Chapter of the Association for Computing Machinery, hereafter
        referred to as ``the Club'', or ``Chapter''.
    \item The Chapter is chartered by the Association for Computing Machinery,
        hereafter referred to as ``ACM''.
    \item The purpose of the Club shall be to:
        \begin{enumerate}
            \item Promote increased knowledge of the science, design,
                development, construction, languages, and applications of modern
                computing machinery.
            \item Promote a greater interest in computing machinery and its
                applications.
            \item Provide a means of communication between persons having
                interest in computing machinery.
        \end{enumerate}
\end{enumerate}

\chapter{Membership}
\section{Classes of Membership} \label{sec:memberclasses}
\begin{enumerate}
    \item Any member of the WPI community as defined by the University is
        eligble for membership.
    \item \label{itm:memberclasses} There shall be three classes of membership in the Chapter: Associate,
        Active, Away, and Alumni.
        \subitem Associate members are any members who do not meet the
        requirements for Active membership.
        \subitem Active members are any members who, within the last
        term, attended at least three Chapter events.
        \subitem Away members are members who have been granted such status by
        the executive board, subject to \cref{itm:awaystatus} of this section.
    \item \label{itm:associate} Any member of the WPI community may become an
        associate member by demonstrating an interest in the Chapter or its
        purpose.
    \item \label{itm:activation} An associate member shall automatically become
        an active member upon fulfilling the requirements listed in
        \cref{itm:memberclasses} of this section.
    \item \label{itm:deactivation} An active member may be deactivated (made
        into an associate member) by the Executive Board if said member no
        longer meets the requirements for active status as specified in
        \cref{itm:memberclasses} of this section.
    \item \label{itm:expulsion} If a member's actions are determined to have
        been detrimental to the Chapter, the Executive Board may revoke said
        member's membership by a simple majority vote of the Board.
    \item \label{itm:awaystatus} An active member who will be absent from the
        University for a defined period of time may petition the Executive
        Board for away status. Members on away status are exempt from the
        active member requirements.
    \item \label{itm:memberalumni} An active member who leaves the University by
        any means shall be automatically reclassified as an Alumni member.
\end{enumerate}

\section{Privileges of Membership}
\begin{enumerate}
    \item Associate and active members are allowed access to Chapter
        infrastructure following policies set by the Executive Board under
        \cref{sec:policies}.
    \item Active members may vote on all issues before the Club. These members
        shall be referred to as the ``voting membership''.
\end{enumerate}

\section{Duties of Membership}
\begin{enumerate}
    \item All members shall at all times uphold all University and Chapter
        policies, in letter and spirit. All members shall hold themselves to the
        ACM Code of Ethics.
    \item All members shall follow in letter and spirit any policies established
        by the Executive Board under \cref{sec:policies}.
\end{enumerate}

\chapter{Executive Board}
\section{Officers}
\begin{enumerate}
    \item The officers of the Chapter shall be President, Vice-President,
        Secretary, Treasurer, Events Coordinator, Public Relations Chair, and
        System Administrator.
    \item The Executive Board shall be composed of all Officers, the Advisor,
        and any appointed positions as determined by the Officers and the
        Advisor.
    \item All officers must be student members of the ACM and active members of
        the Chapter.
    \item Officers shall be elected at the annual Election Meeting. Officers
        shall take office at the second meeting of the Executive Board following
        the Election Meeting and serve until the second Executive Board meeting
        following the next Election Meeting.
    \item No one member shall serve as President or Vice-President for more
        than two consecutive years.
    \item A minimum of two Hackathon Managers are required each year. The
        President and Vice-President can appoint more than two by mutual
        agreement.
    \item Any officer may resign their position by submitting written notice to
        the Executive Board.
    \item In the event the Presidency is vacated, the Vice-President will
        succeed automatically.
    \item Officers may be removed by a 2/3rds majority of either the Executive
        Board or the voting membership. 
\end{enumerate}

\section{Duties of Officers}
\begin{enumerate}
    \item The President shall preside at all meetings of the Chapter
        and the Executive Board. They shall represent the Chapter at all
        meetings with the ACM regional and national leadership. They are
        responsible for representing the organization in all communications and
        meetings with the WPI Computer Science Department.
    \item The Vice-President is responsible for assisting the President in
        carrying out their duties, and taking over for the President as
        required.
    \item The Secretary shall keep minutes of all meetings of the Chapter. They
        shall prepare the Annual Chapter Report prior to the annual Election
        meeting, and present it at said meeting. They shall submit the Annual
        Report to the ACM. They shall keep an accurate record of membership, and
        notify the membership of events and meetings. They shall keep
        CampusGroups up to date with events, members, and officers.
    \item The Treasurer shall collect dues and maintain financial records. They
        shall make the annual report of the Chapter's finances to the Secretary
        for inclusion in the Annual Report. They shall represent the Chapter to
        the Student Government Association for budgeting and special funding
        requests.
    \item The Events Coordinator shall reserve rooms for club events, and serve
        as the point of contact to campus service providers for Chapter events.
        They shall work on improving Chapter events, and be the main planner for
        all Chapter events besides the Hackathon.
    \item The Hackathon Managers shall be the primary planners for the annual
        Hackathon hosted by the Chapter. They are responsible for leading the
        organizing team and ensuring the success of the event.
    \item The Public Relations Chair shall be responsible for raising awareness
        about the Chapter using any effective means. They are responsible for
        maintaining and posting on all social media platforms used by the
        Chapter. They are responsible for logos, branding, and merchandise.
    \item The System Administrator shall be responsible for maintaining the
        Chapter website, mirror service, and all other infrastructure-related
        matters. They shall represent the Chapter in communications with the
        WPI Computer Science Department when said communications relate to
        Chapter infrastructure. They shall also set policies for the use of
        Chapter infrastructure with the assistance of the Executive Board.
\end{enumerate}

\section{Committees}
\begin{enumerate}
    \item The Executive Board shall have the power to create and dissolve such
        committees as they see fit.
    \item Notwithstanding the above section, the Hackathon Committee shall always
        exist. The Hackathon Committee is chaired by the Hackathon Managers, and
        is responsible for the execution of the annual Hackathon.
    \item The President is considered an \emph{ex offico} member of all
        committees.
\end{enumerate}

\section{Interim Officers}
\begin{enumerate}
    \item An office can become vacant through either an Officer being granted
        away status, an Officer submitting their resignation, or an Officer
        being removed from office by the Executive Board or the membership.
    \item A vacancy shall be filled by a Special Election as described in
        \cref{sec:specialelections}.
    \item The Interim Officer shall hold office until the Officer on away status
        returns, the annual Election Meeting, or the Interim Officer submitting
        their resignation, whichever comes first.
\end{enumerate}

\section{Appointed Positions}
\begin{enumerate}
    \item The Executive Board shall have the power to create and dissolve
        appointed positions as they see fit.
    \item Appointed positions shall be filled by active members as described in
        \cref{sec:memberclasses} \cref{itm:memberclasses}. Active members may be
        appointed to or removed from positions at the discretion of the
        Executive Board.
    \item Officers may delegate some of their powers and responsibilities to
        appointed positions as they see fit.
\end{enumerate}

\section{Policies}
\label{sec:policies}
\begin{enumerate}
    \item The Executive Board may create and publish policies to the Chapter
        membership in addition to these Bylaws.
    \item In the event of a conflict between a policy established by the
        Executive Board and these Bylaws, these Bylaws shall take precedence.
\end{enumerate}

\chapter{Meetings}
\begin{enumerate}
    \item Chapter meetings shall be held at least three times per term, as
        determined by the Events Coordinator.
    \item The annual Election Meeting shall be held as the second to last
        meeting of C term. This meeting will consist of the election of all
        officers, and the presentation of the Annual Report by the Secretary.
    \item The Executive Board shall hold weekly planning meetings. These
        meetings should nominally be open to active members.
        \subitem The Executive Board may move to an executive session containing
        only current officers and the Advisor following a successful motion by
        an officer. Executive sessions may involve additional people at the
        discretion of the Executive Board.
    \item Notification of Chapter meetings and activities shall be distributed
        to the membership no later than 24 hours prior to the start of the
        meeting of activity.
    \item For the purposes of conducting votes, a quorum shall be defined as
        greater than 50\% of the voting membership for business meetings, or
        greater than 50\% of the Executive Board for planning meetings. A quorum
        may be composed of members in-person, present via absentee ballot,
        present via online meeting, or any combination of the above.
\end{enumerate}

\chapter{Elections}
\section{Eligibility for Office}
\begin{enumerate}
    \item All officers must be active members as defined in
        section \cref{sec:memberclasses} \cref{itm:memberclasses}.
    \item Any active member who expects to be a full-time undergraduate student
        for the duration of their term of office is eligble for election.
    \item No person may hold more than one office.
\end{enumerate}
\section{Nominations}
\begin{enumerate}
    \item Nominations for elections shall be solicited from the voting
        membership by the Executive Board for the two weeks prior to the Annual
        Election Meeting. 
    \item Nominees must either accept or decline their nomination by the start
        of voting for the position.
    \item In the event that a position receives only one nomination, a
        confidence vote shall be conducted.
\end{enumerate}

\section{Voting} \label{sec:voting}
\begin{enumerate}
    \item Voting shall be conducted by secret ballot. Each ballot should be in
        the form of a ranked list of candidate names or the word ``abstain''.
        Any other text shall count as a vote of no confidence.
    \item \label{itm:tellers} Votes shall be counted by the Teller, who shall be
        either the Chapter Advisor, the Advisor's designee, or a current or
        former member of the Executive Board who is not otherwise participating
        in the election.
    \item Absentee ballots may be accepted in the form of written communication
        of an ordered list of names, the word ``abstain'' or ``no confidence''
        in descending order for each office. This written communication shall be
        submitted to the Teller in accordance with \cref{itm:tellers} of this
        section.
        \subitem If an absentee ballot contains names that have not yet been
        nominated, the Teller shall make a nomination on the absentee's behalf.
    \item Votes will be counted according to the method of Instant Runoff Voting.
\end{enumerate}

\section{Special Elections} \label{sec:specialelections}
\begin{enumerate}
    \item Special Elections shall be conducted as in \cref{sec:voting}, except
        that nominations shall take place in the same meeting as voting.
    \item Special Elections shall be conducted at the first Chapter meeting
        following the vacancy.
\end{enumerate}

\chapter{Advisor}
\begin{enumerate}
    \item The Chapter Advisor shall be selected by the Executive Board with the
        aid of the University and shall be approved by both a 2/3rds majority of
        the voting membership as well as the ACM.
    \item The Advisor will not have voting privileges in any matters.
    \item The Advisor will act as a consultant in matters before the Chapter.
    \item The Advisor may attend meetings and activities of the Chapter as seen
        fit and is entitled to all notifications given to members.
\end{enumerate}

\chapter{Code of Conduct}
\begin{enumerate}
    \item All participants in Chapter activities must follow the University Code
        of Conduct at all times.
\end{enumerate}

\chapter{Parliamentary Authority}
\begin{enumerate}
    \item The rules contained in the current edition of \emph{Robert's Rules of
        Order Newly Revised} shall govern this Chapter in all cases to which
        they are applicable and are not inconsistent with these Bylaws.
    \item In the event that a conflict exists, these Bylaws shall supersede any
        appendix or other Chapter document.
\end{enumerate}

\chapter{Amendments}
\begin{enumerate}
    \item Any active member may propose amendments to these Bylaws or appendices
        thereof to the Executive Board in writing. The Executive Board must
        present all proposed amendments to the Chapter within two weeks of their
        proposal.
    \item A vote to amend these Bylaws must be taken at the next consecutive
        business meeting following notification to the Chapter.
        \subitem A 2/3rds majority of the voting membership is required to pass
        any amendments. Voting will take place by a show of hands for and
        against the proposed amendment.
    \item At least once every two academic years, the Executive Board will
        appoint a committee to review the current Bylaws and, if necessary,
        propose amendments to these Bylaws to the Chapter.
\end{enumerate}

\chapter{SOC Enabling Clause}
The Worcester Polytechnic Institute chapter of the Association for Computing
Machinery agrees to abide by the policies of the Worcester Polytechnic Institute
as well as all federal, state, and local laws. Any changes to these Bylaws shall
follow, in word and spirit, all University policies and all federal, state, and
local laws.

\end{document}
